Future challenges for Research Software Engineering

### 2025-09-22 future_challenges_for_RSEng.tex
change word
"research codebase" sounds a bit strange, especially the plural. I think
just calling it research code sounds better and suffices.

At the same time, we do recognise that the application of core software development best practices
to enhance and address problems with research codebases, that can often make up the bulk of
current RSE work, will change. As noted above, these are skills that we
would expect any researcher who writes code to have in 10 years time. 
The rapid development of artificial intelligence (AI) and large language models
(LLMs) means that researchers are likely to have access to tooling that can assist
them in writing robust, sustainable code, lowering the barrier to developing code,
or at least changing the required skill set to some extent.
They can also be expected to have an understanding of frameworks to support testing, packaging and
deployment of their code as well as integration with central domain specific infrastructures.
Again, all these skills will, we anticipate, be gained as part of training infrastructure that will
provide domain scientists with software development expertise as part of their core scientific training.

>>>>

At the same time, we do recognise that the application of core software development best practices
to enhance and address problems with research code, that can often make up the bulk of
current RSE work, will change. As noted above, these are skills that we
would expect any researcher who writes code to have in 10 years time. 
The rapid development of artificial intelligence (AI) and large language models
(LLMs) means that researchers are likely to have access to tooling that can assist
them in writing robust, sustainable code, lowering the barrier to developing code,
or at least changing the required skill set to some extent.
They can also be expected to have an understanding of frameworks to support testing, packaging and
deployment of their code as well as integration with central domain specific infrastructures.
Again, all these skills will, we anticipate, be gained as part of training infrastructure that will
provide domain scientists with software development expertise as part of their core scientific training.
